Plots for Latent Hawkes Paper

### 2021-08-04 output_scripts/Paper_Plots.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/revision/",
  dev = "png", fig.height = 4.5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

@@

```{r fig-2a-contour-plot, eval=revision_plots}
current_cohort <- 5
# png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(data_path, cohort_names[current_cohort],
  "/cohort_hp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x, y) {
  return(x * y * eta1_mean *
           exp(-eta2_mean * abs(x - y)) / (1 + exp(-eta3_mean * (y - x))))
  # this is because axes are flipped that we have y-x in last term
  # return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(
  seq(1, 0, -0.01),
  seq(0, 1, 0.01),
  z.func
)
my.image.plot(seq(0, 1, 0.01), seq(0, 1, 0.01), z_plot,
  xlab = expression(f[j]), ylab = expression(f[i]),
  my.main = "(a)", cex.main = 2.3,
  cex.lab = 2.5, xLabels = c(1, 0), yLabels = c(0, 1)
)
```

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE, eval=revision_plots}
# current_cohort <- 5
current_cohort <- 5

@@

mtext(
  text = expert_rank_10[[current_cohort]],
  side = 1, line = 1.8, outer = TRUE, cex = 1.8,
  at = 1 / 14 * c(1:12) - 1 / 22
)
mtext(
  text = expert_rank_10[[current_cohort]],
  side = 2, line = 0.5, outer = TRUE, cex = 1.8,
  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
)
mtext(
  text = "(b)", side = 3, line = 1.4, outer = TRUE,
  cex = 2.2,
  at = 0.45, font = 2
)
# dev.off()
ks_chp <- ks.stat.matrix

@@

```{r fig-3a-baseline-rate, eval=revision_plots}
current_cohort <- 5
# current_cohort <- 6 # 3 is maybe ok, 6/7 is interesting

@@

```{r fig-3b-residual-structure, include=TRUE, eval=revision_plots}
### now to add Pearson residual matrices here for C-HP and C-DCHP from fig 7
current_cohort <- 5
data_path <- "../output/revisions/lapl_check/"
## 2 and 8 maybe look better
## 3 probably looks the best

@@

```{r fig3-cohort-response}
current_cohort <- 6

@@

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
  expert_rank_10[[current_cohort]]
],
xLabels = expert_rank_10[[current_cohort]],
yLabels = rev(expert_rank_10[[current_cohort]])
)

@@

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
# current_cohort <- 5
# data_path

@@

@@

```{r fig-7a-pred-all-cohorts-box-mae, fig.width=8,fig.height=4,eval=TRUE}
### updated to revision
load("../output/revisions/lapl_check/plot_N_predict_revision.RData")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/revision/",
  dev = "png", fig.height = 5, fig.width = 7,
  warning = FALSE, cache = TRUE
)

@@

```{r fig-2a-contour-plot, eval=revision_plots, fig.width=6, fig.height=6}
current_cohort <- 5
# png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(data_path, cohort_names[current_cohort],
  "/cohort_hp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x, y) {
  return(x * y * eta1_mean *
           exp(-eta2_mean * abs(x - y)) / (1 + exp(-eta3_mean * (y - x))))
  # this is because axes are flipped that we have y-x in last term
  # return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(
  seq(1, 0, -0.01),
  seq(0, 1, 0.01),
  z.func
)
my.image.plot(seq(0, 1, 0.01), seq(0, 1, 0.01), z_plot,
  xlab = expression(f[j]), ylab = expression(f[i]),
  my.main = "(a)", cex.main = 2.3,
  cex.lab = 2.5, xLabels = c(1, 0), yLabels = c(0, 1)
)
```

@@

```{r fig-2b-diag-plot-c5,echo=FALSE,warning=FALSE, eval=revision_plots, fig.width=6, fig.height=6}
# current_cohort <- 5
current_cohort <- 5

@@

mtext(
  text = expert_rank_10[[current_cohort]],
  side = 1, line = 1.8, outer = TRUE, cex = 1.8,
  at = 1 / 14 * c(1:12) - 1 / 22
)
mtext(
  text = expert_rank_10[[current_cohort]],
  side = 2, line = 0.5, outer = TRUE, cex = 1.8,
  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
)
mtext(
  text = "(b)", side = 3, line = 1.4, outer = TRUE,
  cex = 2.2,
  at = 0.45, font = 2
)
# dev.off()
ks_chp <- ks.stat.matrix
current_cohort <- 6
```

@@

```{r fig-3a-baseline-rate, fig.width=5, fig.height=5, eval=revision_plots}
current_cohort <- 5
## this looks better
# current_cohort <- 6 # 3 is maybe ok, 6/7 is interesting

@@

```{r fig-3b-residual-structure, include=TRUE, fig.width=10, fig.height=5, eval=revision_plots}
### this looks better
### now to add Pearson residual matrices here for C-HP and C-DCHP from fig 7
current_cohort <- 5
data_path <- "../output/revisions/lapl_check/"
## 2 and 8 maybe look better
## 3 probably looks the best

@@

```{r fig3-cohort-response, fig.width=5, fig.height=5}
current_cohort <- 6
### this looks good

@@

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
  expert_rank_10[[current_cohort]]
],
xLabels = expert_rank_10[[current_cohort]],
yLabels = rev(expert_rank_10[[current_cohort]])
)
current_cohort <- 5
```

@@

## Fig 5 Param Recovery

Confirm parameter recovery for some of the simulation settings, as 
a potential figure 5a also.

```{r param-recov}
## param recovery for some lambda0, lambda1, alpha, beta,
## eta1, eta2, eta3
model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3){
  return(eta1 * x * y * exp(-eta2 * abs(x-y))/(1 + exp(-eta3 *(x-y))))})

model3_fn <- list(alpha.fun = function(x, y, eta1, eta2){
  return(eta1*x*y*exp(-eta2*abs(x-y)))},
                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

#### Save the simulation parameters ####

object_fn <- list(alpha.fun = function(x,y,eta1,eta2){
  return(eta1*x*y*exp(-eta2*abs(x-y)))},
                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

num_nodes <- 10
object_par <- list(sim_lambda_1 = 0.6,
                   gamma_var = seq(from = 0.01, to = 0.2,
                                   length.out = num_nodes),
                   zeta_var = rep(0.1, num_nodes),
                   sim_eta_1 = 3, # from 3.5
                   sim_eta_2 = 2,#1.5, # from 2.6
                   sim_eta_3 = 2.5, # 
                   #sim_eta_3 = 7.5,
                   sim_beta = 1.5, # from 2
                   f_vec_1 = seq(from = 0.2,
                                 to = 0.9,
                                 length.out = num_nodes))
object_matrix <- list(
  lambda0_matrix = outer(
    object_par$gamma_var,
    object_par$zeta_var, "+"
  ),
  lambda1_matrix = 1.5*outer(
    object_par$gamma_var,
    object_par$zeta_var, "+"
  ),
  alpha_matrix = formMatrix(
    function(x, y) {
      object_fn$alpha.fun(
        x, y, object_par$sim_eta_1,
        object_par$sim_eta_2
      )
    },
    object_par$f_vec_1
  ),
  beta_matrix = matrix(object_par$sim_beta,
    nrow = length(object_par$f_vec_1),
    ncol = length(object_par$f_vec_1)
  ),
  q1_matrix = formMatrix(
    function(x, y) {
      object_fn$q1.fun(
        x, y,
        object_par$sim_eta_3
      )
    },
    object_par$f_vec_1
  ),
  q2_matrix = formMatrix(
    function(x, y) {
      object_fn$q0.fun(
        x, y,
        object_par$sim_eta_3
      )
    },
    object_par$f_vec_1
  )
)

```{r process-sims}
### load in sims, take mean of each parameter from each simulation 
### setting, add to tibble?
sim_data_path <- here("output", "revisions", "lapl_check", "sim_lapl", "/")

sim_files <- list.files(here("output",
                             "revisions",
                             "lapl_check",
                             "sim_lapl",
                             "/"), 
                        pattern = "sim_model3_fit123_")

par_ests <- tibble()

for(i in seq_along(sim_files)) {
  load(here(
    "output",
    "revisions", 
    "lapl_check",
    "sim_lapl",
    sim_files[i]
  ))
  #then get the ests
  m1_est <- sim_model3_stan_sim1 %>%
    select(beta, eta_1, eta_2, eta_3) %>% 
    summarise(across(.cols = everything(), median)) %>%
    pivot_longer(cols = everything()) %>% 
    mutate(sim_id = i, model = "C-HP")

  m2_est <- sim_model3_stan_sim2 %>%
    select(beta, eta_1, eta_2, eta_3,
           starts_with("gamma"),
           starts_with("zeta")) %>% 
    summarise(across(.cols = everything(), median)) %>%
    pivot_longer(cols = everything()) %>% 
    mutate(sim_id = i, model = "C-DCHP")

  m3_est <- sim_model3_stan_sim3 %>%
    select(beta, eta_1, eta_2, eta_3, 
           starts_with("gamma"),
           starts_with("zeta")) %>% 
    summarise(across(.cols = everything(), median)) %>%
    # rename(w_lambda = r_lambda1) %>% 
    pivot_longer(cols = everything()) %>% 
    mutate(sim_id = i, model = "C-MMHP")
  par_ests <- par_ests %>% bind_rows(m1_est, m2_est, m3_est)
}

par_ests

true_pars <- tibble(name = c("beta", "eta_1", "eta_2", "eta_3",
                             paste0("gamma[", 1:10, "]"),
                             paste0("zeta[", 1:10, "]")),
                    value = c(1.5, 3, 2, 2.5, seq(from = 0.01, to = 0.2,
                                   length.out = num_nodes),
                              rep(0.1, num_nodes)))

par_ests %>% 
  filter(name %in% c("beta", "eta_1", "eta_2", "eta_3")) %>% 
  ggplot(aes(model, value)) + geom_boxplot() +
  geom_hline(data = true_pars %>% 
               filter(name %in% c("beta", "eta_1", "eta_2", "eta_3")),
             aes(yintercept = value)) +
  facet_wrap(vars(name), scales = "free")

par_ests %>% 
  filter(!name %in% c("beta", "eta_1", "eta_2", "eta_3")) %>% 
  ggplot(aes(model, value)) + geom_boxplot() +
  geom_hline(data = true_pars %>%
               filter(!name %in% c("beta", "eta_1", "eta_2", "eta_3")),
             aes(yintercept = value)) +
  facet_wrap(vars(name), scales = "free")

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 5
# data_path

@@

# Further results on latent ranks

Wish to investigate some further properties of the
latent states for these animals, in the context of the above latent rank
plot.

```{r prop-active-inactive, eval=FALSE}
### think need to run this
current_cohort <- 6
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort,
  raw_df =
    full_data[[cohort_names[current_cohort]]],
  clean_data
)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

load(paste(data_path, cohort_names[current_cohort],
  "/cmmhp_est_zt_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))

### then look at these pairwise
length(interpolation_array_list)

dim(interpolation_array_list[[1]][[1]]) # each column here is a simulation
num_pairs <- length(interpolation_array_list)
num_winds <- length(interpolation_array_list[[4]])

## 500 for each window

mean_state <- matrix(NA, nrow = num_pairs, ncol = num_winds)

for(i in seq_along(1:num_pairs)) {
  for(j in seq_along(1:num_winds)) {
    if(i != 19) { # self directed event, remove
      curr_mean_vec <- apply(interpolation_array_list[[i]][[j]],
                                    1, mean)
      mean_state[i,j] <- mean(curr_mean_vec)
    }
  }
}
# apply(interpolation_array_list[[i]][[j]], 1, mean)
# dim(interpolation_array_list[[i]][[j]])

# then just take mean state, multiply by length of the window...
dim(unique_observe_win)

### this is the expected amount of time in the active state?
prop_active <- mean_state %*% 
  unique_observe_win$observe.time# /sum(unique_observe_win$observe.time)

prop_active[is.na(prop_active)] <- 0

pairs_tibble <- unique_pairs_df
pairs_tibble$prop_active <- prop_active

init_act <- pairs_tibble %>% group_by(initiator) %>% 
  summarise(mean_active = sum(prop_active)) %>% 
  arrange(desc(mean_active))

rec_act <- pairs_tibble %>% group_by(recipient) %>% 
  summarise(mean_active = sum(prop_active)) %>% 
  arrange(desc(mean_active))

bind_rows(init_act %>% rename(start = initiator),
          rec_act %>% rename(start = recipient)) %>% 
  group_by(start) %>% 
  summarise(total_active = sum(mean_active)) %>% 
  arrange(total_active)

```{r rerun-isi, eval=FALSE}
num_tries <- 100 
result <- matrix(NA, nrow = num_tries, ncol = 12)
for(i in 1:num_tries){
  print(i)
  raw_data <- full_data[[cohort_names[current_cohort]]]
  win_lost_df <- raw_data[-which(raw_data[,
                                        "Actor"]=="Start"|raw_data[,
                                                              "Actor"]=="End"),
                          c("Actor","Recipient")]
  win_lost_matrix <- get_wl_matrix(win_lost_df)
  sample
  # problem is that the initial rank the same the whole time.
  win_lost_matrix
  out <- isi98(win_lost_matrix[gtools::permute(1:12), gtools::permute(1:12)])
  a <- as.numeric(out$best_order)

  result[i, ] <- a
}

result[ ,12]

```{r explore-cohort, eval=FALSE}
unique_pairs_df %>% 
  group_by(initiator) %>% 
  summarise(start = sum(count)) %>% 
  arrange(start)

unique_pairs_df %>% 
  group_by(recipient) %>% 
  summarise(receive = sum(count)) %>% 
  arrange(receive)

### look at out degree estimates also
sim_cohort_mmhp %>% 
  select(starts_with("gamma")) %>% 
  summarise(across(everything(), mean)) %>% 
  pivot_longer(everything())

sim_cohort_mmhp %>% 
  select(starts_with("zeta")) %>% 
  summarise(across(everything(), mean)) %>% 
  pivot_longer(everything())

### get sd for each of the 3 models

m1 <- sim_cohort_hp %>% 
  select(starts_with("f")) %>% 
  summarise(across(everything(), sd)) %>% 
  pivot_longer(everything()) %>% 
  mutate(model = "C-HP")

m2 <- sim_cohort_dchp %>% 
  select(starts_with("f")) %>% 
  summarise(across(everything(), sd)) %>% 
  pivot_longer(everything()) %>% 
  mutate(model = "C-DCHP")

m3 <- sim_cohort_mmhp %>% 
  select(starts_with("f")) %>% 
  summarise(across(everything(), sd)) %>% 
  pivot_longer(everything()) %>% 
  mutate(model = "C-MMHP")

bind_rows(m1, m2, m3) %>% 
  left_join(m3, by = "name") %>% 
  rename(mmhp_var = value.y, var = value.x) %>% 
  select(-model.y) %>% 
  group_by(name) %>%
  summarise(per_var = var/mmhp_var, model = model.x) %>% 
  filter(model != "C-MMHP") %>% 
  # ungroup() %>% 
  # pull(per_var)
  mutate(per_var_cmmhp = scales::percent(per_var)) %>% 
  select(-per_var)
```

## Further rank information

```{r compute-isi-using-cmmhp-ranking, eval=FALSE}
f_med <- sim_cohort_mmhp %>% 
  select(starts_with("f")) %>% 
  summarise(across(everything(), median)) %>% 
  pivot_longer(everything())

isi_ord <- order(f_med$value,decreasing = TRUE)

df <- win_lost_df
df[, 1] <- factor(df[, 1], levels = 1:12)
df[, 2] <- factor(df[, 2], levels = 1:12)
df$result <- 1
m1 <- stats::xtabs(result ~ ., data = df)

result <- isi98(m1[isi_ord,isi_ord])
```

```{r investigate-bursty, eval=FALSE}
# inter_8_10 <-

theme_set(theme_minimal())

return_df %>% 
  filter(initiator == 7) %>% 
  select(initiator, 
         recipient,
         observe.id,
         observe.start,
         observe.end,
         event.times) %>% 
  unnest_longer(event.times) %>% 
  group_by(observe.id, initiator) %>% 
  arrange(event.times, .by_group = TRUE) %>% 
  mutate(inter = event.times - lag(event.times, default = 0)) %>% 
  ggplot(aes(inter)) + geom_histogram() +
  labs(title = "Fights from animal 12")

return_df %>% 
  filter(recipient == 7) %>% 
  select(initiator, 
         recipient,
         observe.id,
         observe.start,
         observe.end,
         event.times) %>% 
  unnest_longer(event.times) %>% 
  group_by(observe.id, initiator) %>% 
  arrange(event.times, .by_group = TRUE) %>% 
  mutate(inter = event.times - lag(event.times, default = 0)) %>% 
  ggplot(aes(inter)) + geom_histogram() +
  labs(title = "Fights to animal 12")

return_df %>% 
  filter(initiator %in% c(3) | recipient == 3) %>% 
  select(initiator, 
         recipient,
         observe.id,
         observe.start,
         observe.end,
         event.times) %>% 
  unnest_longer(event.times) %>% 
  group_by(observe.id, initiator) %>% 
  arrange(event.times, .by_group = TRUE) %>% 
  mutate(inter = event.times - lag(event.times, default = 0)) %>% 
  ggplot(aes(inter)) + geom_histogram() + 
  labs(title = "Top Ranked Animals")

```{r investigate-animal-12, eval=FALSE}
### want to try establish what proportion of its fights occur in inactive
### periods compared to other animals, etc
cur_node <- 12

pairs <- unique_pairs_df %>% 
  ungroup() %>% 
  mutate(index = row_number()) %>% 
  filter(initiator == cur_node) %>% 
  select(index, initiator, recipient, observe) %>%
  # observe gives the window its in
  # unnest_wider(observe) %>%
  pull(index)

observe_winds <- unique_pairs_df %>% 
  ungroup() %>% 
  mutate(index = row_number()) %>% 
  filter(initiator == cur_node) %>% 
  select(index, initiator, recipient, observe)

## need to somehow get the corresponding entries of the matrix 
## for these
for(i in seq_along(1:nrow(observe_winds))) {
  curr_winds <- observe_winds$observe[[i]]
  print(mean_state[pairs, ][i, curr_winds])
}

### how do these differ?

###
### this is the mean state across all observation windows, compared
### to the mean state for windows where events are observed above
apply(mean_state[pairs, ], 1, mean)

###  
act_vec <- mean_state %*% 
  unique_observe_win$observe.time
act_vec[pairs] /sum(unique_observe_win$observe.time)
```

### Explore Latent States

Look at fights from/to a given animal and plot the inferred latent 
states for each window.

```{r plot-latent-given-animal, eval=FALSE}
# dim(interpolation_array_list[[1]][[1]])
# ### pair then window then segment times simulation
# 
# interpolation_array_list[[1]][[1]][1 , ] %>% 
#   map_dbl(., mean)
# 
# ### need a function to take a given
# 
# ### this is what I want
# dim(interpolation_array_list[[1]][[1]])
# apply(interpolation_array_list[[1]][[1]], 1, mean) 
# # want to do this for each pair

mean_states <- function(df) {
  return(apply(df, 1, mean))
}

pair_list <- unique_pairs_df %>% 
  ungroup() %>% 
  mutate(index = row_number()) %>% 
  filter(initiator == 12) %>% 
  pull(index)

pair_list

num_pairs <- nrow(unique_pairs_df)
pair_result <- vector(mode = "list", length = num_pairs)

for(i in seq_along(1:num_pairs)) {
  if(i != 19) {
    print(i)
    pair_result[[i]] <- interpolation_array_list[[i]] %>% 
    map(~mean_states((.x))) %>% 
    set_names(paste0("window_", 1:34)) %>% 
    as_tibble()
  }
}

pair_result # has for each pair in each element
saveRDS(pair_result, file = "pair_result.RDS")
```

Look at the output from this process, plot these, etc.

```{r look-at-pair-result, eval=FALSE}
pair_result <- readRDS("../pair_result.RDS")
theme_set(theme_minimal())

### need to get the event times within windows also...
# return_df %>% 
#   select(observe.id, initiator, recipient, event.times)
# 
# unique_observe_win
# ## this is everything I need for the plots then...
# unique_pairs_df %>% 
#   ungroup() %>% 
#   mutate(index = row_number()) %>% 
#   filter(initiator == init & recipient == rec) %>% 
#   pull(index)

plot_window <- function(init, rec) {
  res_state_tibb <- tibble()
  res_event_tibb <- tibble()
  pair <- unique_pairs_df %>% 
            ungroup() %>% 
            mutate(index = row_number()) %>% 
            filter(initiator == init & recipient == rec) %>% 
            pull(index)
  if(length(pair) == 0) {
    stop("No interactions")
  }
  for(window in 1:34) {
    state_vec <- pair_result[[pair]][, window] 
    state_vec <- state_vec %>% pull(names(state_vec))
    length_wind <- unique_observe_win$observe.time[window]
    init <- unique_pairs_df$initiator[pair]
    rec <- unique_pairs_df$recipient[pair]
    events <- return_df %>% 
      filter(initiator == init) %>% 
      filter(recipient == rec) %>% 
      filter(observe.id == window) 
    if(nrow(events) > 0 ) {
      event_times <- unlist(events$event.times)
      event_tibb <- tibble(x = event_times, y = 0, wind = window)
      res_event_tibb <- res_event_tibb %>% 
        bind_rows(event_tibb)

      state_tibb <- tibble(x = seq(from = 0,
                                   to = length_wind,
                                   length.out = 500),
                           mean_state = state_vec,
                           wind = window)
      res_state_tibb <- res_state_tibb %>% 
      bind_rows(state_tibb)
    } 
  }
  ### could do a facet wrap by window! 
  plt <- res_state_tibb %>% 
  ggplot(aes(x, mean_state)) +
  geom_line(aes(colour = "Mean State")) +
  geom_point(data = res_event_tibb, mapping = aes(x,y)) +
  facet_wrap(~wind, scales = "free_x") +
  scale_y_continuous(breaks = c(0, 1)) +
  # scale_x_continuous(breaks = c(1, 2)) +
  theme(legend.title = element_blank(), axis.text.x = element_blank()) +
  labs(x = "Time", y = "Latent State",
       title = paste("From", init, "to", rec))
  print(plt)
}

We can then look at some of these for some pairs of interest.

```{r from-12, eval=FALSE}
## make sure correct return_df loaded here
plot_window(12, 1)
plot_window(12, 2)
plot_window(12, 3)
plot_window(12, 4)
plot_window(12, 5)
plot_window(12, 6)
plot_window(12, 7)
plot_window(12, 8)
plot_window(12, 9)
plot_window(12, 10)
plot_window(12, 11)
```

```{r to-animal-12, eval=FALSE}
# plot_window(1, 12)
# plot_window(2, 12)
plot_window(3, 12)
plot_window(4, 12)
plot_window(5, 12)
# plot_window(6, 12)
# plot_window(7, 12)
plot_window(8, 12)
plot_window(9, 12)
plot_window(10, 12)
plot_window(11, 12)
```

Similarly, we can look at the breakdown of events that are classified as
active as opposed to inactive.

```{r classify-events, eval=FALSE}
total_event_array <- array(0,
                           dim = c(mice_number, mice_number,
                                   max(return_df$observe.id)))
active_event_array <- array(0,
                            dim = c(mice_number, mice_number,
                                    max(return_df$observe.id)))

for (i in 1:mice_number) {
  for (j in 1:mice_number) {
    if(i != j) {
      pair <- which(unique_pairs_df$initiator == i & 
                      unique_pairs_df$recipient == j)
      if (length(pair) > 0) {
        current_window_vec <- unique_pairs_df$observe[[pair]]
        for (cur_win in current_window_vec) {
          row_indicator <- (return_df$initiator == i) &
            (return_df$recipient == j) &
            (return_df$observe.id == cur_win)
          total_event_array[i, j, cur_win] <- length(return_df[row_indicator,
                                                            "event.times"][[1]])
          active_event_array[i, j, cur_win] <- sum(apply(2 -
                                           state_array_list[[pair]][[cur_win]],
                                           1, mean) > 0.5)
        }
      }
    }
  }
}

total_matrix <- apply(total_event_array, c(1,2), sum)
active_matrix <- apply(active_event_array, c(1,2), sum)

inact_matrix <- total_matrix - active_matrix

### compute isi for each
names(active_matrix) <- 1:12
colnames(active_matrix) <- 1:12
rownames(active_matrix) <- 1:12
isi98(active_matrix)

names(inact_matrix) <- 1:12
colnames(inact_matrix) <- 1:12
rownames(inact_matrix) <- 1:12
isi98(inact_matrix)
```

@@

```{r fig-7a-pred-all-cohorts-box-mae,eval=TRUE, fig.width=8, fig.height=4}
### updated to revision
load("../output/revisions/lapl_check/plot_N_predict_revision.RData")
